---
title: "Final Proposal"
author: "Chloe Wong, Hanwen Yang, Junhao Lai"
date: '2024-03-01'
output:
  pdf_document: 
    number_sections: true
---

```{r setup, include=FALSE}
# some useful settings
knitr::opts_chunk$set(echo = TRUE, tidy.opts = list(width.cutoff = 55), tidy = TRUE, fig.align="center")
```

# Introduction 

Our research looks at how the quality of living arrangements affects how satisfied older adults are with their lives, especially during the COVID-19 economic downturn. We're using data from a study focusing on people aged 55 and up during the early stages of the pandemic, "https://www.openicpsr.org/openicpsr/project/131022/version/V3/view?path=/openicpsr/131022/fcr:versions/V3/C19CS-Data-Labeled.xlsx&type=file"
The main question we want to find out is whether there's a direct link between living conditions and life satisfaction, in other words we are using this public data to study the casual effect on its life satisfaction rating based on how good someone's living situation is. We're focusing on how people rate their own health as our main measure (Y), and one thing we're looking at is how likely it is that they'll run out of money because of COVID-19 (X). We're using different statistical methods like simple logit regression and post-lasso to figure out these relationships and understand how living conditions, health, and happiness are connected during tough economic times.
  

```{r}
#setwd("/Users/laix1/OneDrive/Desktop/Final_Proposal")
knitr::opts_knit$set(root.dir = 'C:/Users/laix1/OneDrive/Desktop/final/ECON124')

library(haven)

covid_data <- data.frame(read_dta("C19CS Data.dta"))


dim(covid_data)
colnames(covid_data)[c(204,451)]
```
```{R}
#names(covid_data)
```

## Part (b)


# Data



# Methodology 


# Main Results
we first did a raw correlation on the smoking status and COVID-19 positivity 
```{r}

SM_data <- na.omit(covid_data[,c(201,851),]) #
head(SM_data)

naive_SM_OLS <- glm(t5_cov_self_t ~ t0_smoke, data = SM_data)
summary(naive_SM_OLS)



```
A person what has an active smoking status is associated with a 2.4% increased in the chance of tested positive for COVID-19 past month.

