---
title: "Final Proposal"
author: "Chloe Wong, Hanwen Yang, Junhao Lai"
date: '2024-03-01'
output:
  pdf_document: 
    number_sections: true
---

```{r setup, include=FALSE}
# some useful settings
knitr::opts_chunk$set(echo = TRUE, tidy.opts = list(width.cutoff = 55), tidy = TRUE, fig.align="center")
```

# Introduction 

The dataset, available at "https://www.openicpsr.org/openicpsr/project/131022/version/V3/view?path=/openicpsr/131022/fcr:versions/V3/C19CS-Data-Labeled.xlsx&type=file", focuses on adults nearing retirement age who have been particularly impacted by the recent economic downturn due to COVID-19. The research examines how the early stages of the pandemic have disrupted the work lives and mental health of Americans aged 55 and older.
  In our research, we want to find ....(will be finished  tentative) the correlation betweenthe outcome variable tested positive for covid-19 in the past month (y) and their smoking status as one of the regressor (x).    
  
  

```{r}
#setwd("/Users/laix1/OneDrive/Desktop/Final_Proposal")
knitr::opts_knit$set(root.dir = 'C:/Users/laix1/OneDrive/Desktop/Final_Proposal/ECON124')

library(haven)

covid_data <- data.frame(read_dta("C19CS Data.dta"))


dim(covid_data)


```
```{R}
names(covid_data)
```

## Part (b)


# Data



# Methodology 


# Main Results
we first did a raw correlation on the smoking status and COVID-19 positivity 
```{r}

SM_data <- na.omit(covid_data[,c(201,851),]) #
head(SM_data)

naive_SM_OLS <- glm(t5_cov_self_t ~ t0_smoke, data = SM_data)
summary(naive_SM_OLS)



```
A person what has an active smoking status is associated with a 2.4% increased in the chance of tested positive for COVID-19 past month.

